\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-26 syntax.tex
Reply the comments.

@@

\begin{figure}[!htb]
  \begin{alignat*}{3}
    \text{Inductive Type Signature}   \quad & \tau       &&= w\cdot~|~w^+~\tau~A~B~|~\tau[\gamma] \\
    \text{Linkage Signature}          \quad & \sigma       &&= \nu\cdot~|~\nu^+~\sigma~\{f\}~T~|~\sigma[\gamma]~|~p_1\nu~\sigma \\
    \text{Seal}          \quad & f       &&= t~|~p_f\nu'~\sigma\\    
    \text{Types}   \quad & A, B, T        &&= \bW \tau~|~\pi_1^j~|~\pi_2^j~|~\cL\sigma~|~\cC\sigma~|~p_1\nu'~\sigma~|~p_2\nu~\sigma\YZ{No universes? And what is p1 nu′?}\\
    \text{Terms}   \quad & t, t_1, t_2    &&= "W"~T~|~"Wsup"~T~t_1~t_2~|~\mu\cdot~|~\mu^+~t~\{f\}~T~|~p_1\mu~t~|~p_2\mu~t~|~\cCt~t
  \end{alignat*}
\caption{Overview of Instrinsically-typed Syntax for extended MLTT}
\end{figure}
\begin{figure}[!htb]
  \begin{align*}
&\sigma~:~"Sig"~\Gamma~n&&\mathboxtext{\goodSig{\Gamma}{\sigma}{n}}  &&\tau~:~"WSig"~\Gamma~n&&\mathboxtext{\goodWSig{\Gamma}{\tau}{n}} \\ &h~:~"Inh"~\Gamma~\sigma_1~\sigma_2&&\mathboxtext{\goodInh{\Gamma}{h}{\sigma}{\tau}} && f~:~"Seal"~\Gamma~\sigma~T&&\mathboxtext{\goodSeal{\Gamma}{f}{\sigma}{A}}\YZ{A little unfriendly to the reader that there are three different things that sigma can range over. Besides, later you also use gamma to range over substitutions and s to range over W-types, which add to the confusion.}\EDJreply{Fair point. I have fixed fix sigma and tau to be about signatures and W signature, and use gamma as substitutions}
  \end{align*}
\caption{Extended Judgement forms, as Agda types}
\end{figure}
\begin{figure}[!htb]
  \begin{minipage}[b]{0.3\linewidth}
      $$
      \Rule[name=Sig]
      {\goodCtx{\Gamma}{i} \quad n \in \nat}
      {\goodSig{\Gamma}{\_}{n} \text{ is well-formed}}
      $$
      $$
      \Rule[name=Seal]
      {\goodCtx{\Gamma}{i} \quad \goodSig{\Gamma}{\sigma}{n} 
      \quad \goodType{\Gamma}{A}{} }
      {\goodSeal{\Gamma}{\_}{\sigma}{A} \text{ is well-formed}}
      $$\YZ{Doesn't the left column show well-formedness rules for ONLY TWO of the four new judgments? Besides, are these rules used anywhere in the following? Seems a bit unusual to have well-formedness rules for judgments per se.}\EDJreply{Yes. Right column show all the well-formedness rule for all the judgement. That is unusual because it is a direct translation from QIIT. }
  \end{minipage}
  \begin{minipage}[b]{0.6\linewidth}
    \begin{minted}[]{agda}
      data Sig  : Con → ℕ → Set
      data WSig : Con → ℕ → Set 
      data Inh  : (Γ : Con) → Sig Γ n → Sig Γ m → Set
      Seal : (Γ : Con) → Sig Γ n → Sig Γ n → Set
    \end{minted}
  \end{minipage}

@@

$$
\Rule[name=Compile]
{}
{\goodType{\Gamma}{\cC \nu\cdot \equiv \top}{} 
\\
\goodType{\Gamma}{\cC (\nu^+ \ \sigma \ \{f\} \ T) \equiv 
    \Sigma (\cC \sigma) T["sf" \ f]}{}
\\\\ \goodTerm{\Gamma}{ \cCt \mu\cdot \equiv ()}{\cL \nu\cdot}\YZ{cL or cC?}
\\ \goodTerm{\Gamma}{\cCt \ (\mu^+ \ o \ \{f\}\ t) \equiv ((\cCt \ o), t["sf" \ f][(id, \cCt \ o)]) }{}\YZ{nothing after colon?}
}
$$
% $$
% \Rule
% { \goodSeal{\Gamma}{f}{\sigma}{A}
% \\ \goodType{\Gamma, A}{T}{}
% \\ \goodTerm{\Gamma}{t}{T}
% }{}
% $$

>>>>

We also have identity type as part of our core syntax from the original MLTT. but we omit its presentations here---we follow~\citet{kaposi2019gluing} and use based path induction~\citet{program2013homotopy} as the elimination rule.

@@

\begin{figure}[!htb]
  \begin{alignat*}{3}
    \text{Inductive Type Signature}   \quad & \tau       &&= w\cdot~|~w^+~\tau~A~B~|~\tau[\gamma] \\
    \text{Linkage Signature}          \quad & \sigma       &&= \nu\cdot~|~\nu^+~\sigma~\{f\}~T~|~\sigma[\gamma]~|~p_1\nu~\sigma \\
    \text{Seal}          \quad & f       &&= t~|~p_f\nu'~\sigma\\    
    \text{Types}   \quad & A, B, T        &&= ...~|~\bW \tau~|~\pi_1^j~|~\pi_2^j~|~\cL\sigma~|~\cC\sigma~|~p_1\nu'~\sigma~|~p_2\nu~\sigma\YZ{No universes? And what is p1 nu′?}\EDJreply{Universe is described in Figure 9.``Overview of Instrinsically-typed Syntax for vanilla MLTT``. p_1 nu' is getting the resulting abstracted type after sealing. You can see that from Sig Proj rule.}\\
    \text{Terms}   \quad & t, t_1, t_2    &&= ...~|~"W"~T~|~"Wsup"~T~t_1~t_2~|~\mu\cdot~|~\mu^+~t~\{f\}~T~|~p_1\mu~t~|~p_2\mu~t~|~\cCt~t
  \end{alignat*}
\caption{Overview of Instrinsically-typed Syntax for extended MLTT}
\end{figure}
\begin{figure}[!htb]
  \begin{align*}
&\sigma~:~"Sig"~\Gamma~n&&\mathboxtext{\goodSig{\Gamma}{\sigma}{n}}  &&\tau~:~"WSig"~\Gamma~n&&\mathboxtext{\goodWSig{\Gamma}{\tau}{n}} \\ &h~:~"Inh"~\Gamma~\sigma_1~\sigma_2&&\mathboxtext{\goodInh{\Gamma}{h}{\sigma}{\tau}} && f~:~"Seal"~\Gamma~\sigma~T&&\mathboxtext{\goodSeal{\Gamma}{f}{\sigma}{A}}\YZ{A little unfriendly to the reader that there are three different things that sigma can range over. Besides, later you also use gamma to range over substitutions and s to range over W-types, which add to the confusion.}\EDJreply{Fair point. I have fixed fix sigma and tau to be about signatures and W signature, and use gamma as substitutions}
  \end{align*}
\caption{Extended Judgement forms, as Agda types}
\end{figure}
\begin{figure}[!htb]
  \begin{minipage}[b]{0.3\linewidth}
      $$
      \Rule[name=Sig]
      {\goodCtx{\Gamma}{i} \quad n \in \nat}
      {\goodSig{\Gamma}{\_}{n} \text{ is well-formed}}
      $$
      $$
      \Rule[name=Seal]
      {\goodCtx{\Gamma}{i} \quad \goodSig{\Gamma}{\sigma}{n} 
      \quad \goodType{\Gamma}{A}{} }
      {\goodSeal{\Gamma}{\_}{\sigma}{A} \text{ is well-formed}}
      $$\YZ{Doesn't the left column show well-formedness rules for ONLY TWO of the four new judgments? Besides, are these rules used anywhere in the following? Seems a bit unusual to have well-formedness rules for judgments per se.}\EDJreply{Yes. Right column show all the well-formedness rule for all the judgement. That is unusual because it is a direct translation from QIIT. }
  \end{minipage}
  \begin{minipage}[b]{0.6\linewidth}
    \begin{minted}[]{agda}
      data Sig  : Con → ℕ → Set
      data WSig : Con → ℕ → Set 
      data Inh  : (Γ : Con) → Sig Γ n → Sig Γ m → Set
      Seal : (Γ : Con) → Sig Γ n → Sig Γ n → Set
    \end{minted}
  \end{minipage}

@@

$$
\Rule[name=Compile]
{}
{\goodType{\Gamma}{\cC \nu\cdot \equiv \top}{} 
\\
\goodType{\Gamma}{\cC (\nu^+ \ \sigma \ \{f\} \ T) \equiv 
    \Sigma (\cC \sigma) T["sf" \ f]}{}
\\\\ \goodTerm{\Gamma}{ \cCt \mu\cdot \equiv ()}{\cC \nu\cdot}\YZ{cL or cC?}\EDJreply{cC. You are right.}
\\ \goodTerm{\Gamma}{\cCt \ (\mu^+ \ o \ \{f\}\ t) \equiv ((\cCt \ o), t["sf" \ f][(id, \cCt \ o)]) }{}\YZ{nothing after colon?}\EDJreply{There should be something but the space is not enough.}
}
$$
% $$
% \Rule
% { \goodSeal{\Gamma}{f}{\sigma}{A}
% \\ \goodType{\Gamma, A}{T}{}
% \\ \goodTerm{\Gamma}{t}{T}
% }{}
% $$
